Analysis of the 2005--\myrevision{2016} Earthquake Sequence in Northern Iran Using the Visibility Graph Method

### 2017-06-22 results.tex
general fixes

\begin{figure*}%[t]
	\centering
	\includegraphics[width=\textwidth]{figures/pdf/figure-09} 
	\caption{\myrevision{Variation of $<$$T_c$$>$, $k$-$M$ slope ($m$) and the $b$ value with respect to time for the seismic zone of Alborz for a moving window analysis of the visibility graphs of subsequences of $n=50$ consecutive events, along with the magnitude and the connectivity degree ($k$) of events in the 2005--2016 period. Black triangles indicate the occurrence of significant earthquakes in each of the regions, with the corresponding magnitude at the top of each symbol.}}
	\label{fig:tc}
\end{figure*}

@@

\myrevision{In this windowing analysis, in addition to $b$ and $m$, we are interested in computing the value of $<$$T_c$$>$ explained in the Methodology section. Figure \ref{fig:tc} shows the earthquake sequence for the region of Alborz, and the variation of $k$, $m$, $b$, and $<$$T_c$$>$ with time. Although we performed the analysis for all three seismic zones, we concentrate in the region of Alborz because is the one with the larger number of events for the fixed-size moving window. We can see here how larger values of $k$ are associated with the larger magnitude earthquakes, and how the resulting values of $m$ for each 50-event sequence compares with $b$. In particular, we observe a good correlation between $m$ and $b$ for the period prior to the 2010 $M_w$ 5.8 Damaghan earthquake, but after this event the correlation is not as clear. We do not observe any clear correlation between the behavior of $<$$T_c$$>$ and the occurrence of the larger magnitude ($M_w \geq 5$) earthquakes in this region. Furthermore, while the occurrence of larger events does seem to coincide with drops in $m$ and $b$, there are other similar changes in the values of $m$ and $b$ that are not associated with any significant event, making it difficult to draw strong conclusions. Nonetheless, in the region of Azerbaijan, we did observe more prominent changes in $m$ and $b$ with the occurrence of the 2012 $M_w$ 6.4 Tabriz earthquake, which leaves open the possibility to further study this for regions with larger magnitude events.}

\begin{figure*}[t]
	\centering
	\includegraphics[width=\textwidth]{figures/pdf/figure-10} 
	\caption{\myrevision{Correlation between $m$ and $b$ based on the fixed-size windowing analysis done for the region of Alborz, for both the complete (a) and declustered (b) catalogs, along with the linear regressions of each case. While a direct comparison is not appropriate, the universal regression is shown as well for reference.}}
	\label{fig:alborz-bm}
\end{figure*}

\myrevision{Finally, we explore the correlation between $k$ and $b$ by aggregating the results of the windowing analysis. Figure \ref{fig:alborz-bm}a shows condensed (scattered) results for all the values $k$ and $b$ from Fig.~\ref{fig:tc} for the complete catalog of Alborz, and Fig.~\ref{fig:alborz-bm}b shows the same results but for the declustered catalog. Both plots exhibit reasonable linear regressions for an ample range of $m$ and $b$ values. While it is not entirely fair to compare these results (which are exclusive to the Alborz region) with the universal results discussed before, Fig.~\ref{fig:alborz-bm} also includes the universal correlations for reference. The results for Alborz also show $b$ to increase proportionally with $m$, although at a smaller rate.}

>>>>

\begin{figure*}%[t]
	\centering
	\includegraphics[width=\textwidth]{figures/pdf/figure-09} 
	\caption{\myrevision{Variation of $<$$T_c$$>$, $k$-$M$ slope ($m$) and the $b$ value with respect to time for the seismic regions of Azerbaijan (a) and Alborz (b) considering a moving window analysis of the visibility graphs of subsequences of $n=50$ consecutive events, along with the magnitude and the connectivity degree ($k$) of events in the 2005--2016 period. Black triangles indicate the occurrence of significant earthquakes in each of the regions, with the corresponding magnitude at the top of each symbol.}}
	\label{fig:tc}
\end{figure*}

@@

\myrevision{In this windowing analysis, in addition to $b$ and $m$, we are interested in computing the value of $<$$T_c$$>$ explained in the Methodology section. Figure \ref{fig:tc} shows the earthquake sequence for the regions of Azerbaijan and Alborz, and the variation of $k$, $m$, $b$, and $<$$T_c$$>$ with time. Although we performed the analysis for all three seismic zones, we concentrate in this two regions because the windowed sequence of Kopeh Dagh was too short and did not add value to the discussion. In the two cases in Fig.~\ref{fig:tc} we can see here how larger values of $k$ are associated with the larger magnitude earthquakes, and how the resulting values of $m$ for each 50-event sequence compares with $b$. For the case of Alborz, we observe a good correlation between $m$ and $b$ for the period prior to the 2010 $M_w$ 5.8 Damaghan earthquake, but after this event the correlation is not as clear. For Azerbaijan, the relationship between $m$ and $b$ is less evident, except for the timespan around the occurrence of the 2012 $M_w$ 6.4 Tabriz earthquake, in which case both all three parameters ($b$, $m$ and $<$$T_c$$>$) show a clear drop in their values. By contrast, in the case of Alborz, we do not observe any clear correlation between the behavior of $<$$T_c$$>$ and the occurrence of the largest ($M_w \geq 5$) earthquakes in this region. We notice that while the occurrence of the larger events does seem to coincide with drops in $m$ and $b$, there are other similar changes in the values of $m$ and $b$ that are not associated with any significant event, making it difficult to draw strong conclusions solely based on the results for the region of Azerbaijan and the 2012 Tabriz earthquake. It is possible, however, that regions with larger events or catalogs with lower $M_c$ lead to better insight on this matter.}

\begin{figure*}[t]
	\centering
	\includegraphics[width=\textwidth]{figures/pdf/figure-10} 
	\caption{\myrevision{Correlation between $m$ and $b$ based on the fixed-size windowing analysis done for the regions of Azerbaijan (a) and Alborz (b), along with the linear regressions of each case. While a direct comparison is not appropriate, the universal regression is shown here for reference.}}
	\label{fig:azal-bm}
\end{figure*}

\myrevision{The better correlation observed between $m$ and $b$ for Alborz than for Azerbaijan is further explored in Fig.~\ref{fig:azal-bm}, which presents the condensed (scattered data-point) results for all the values $k$ and $b$ from Fig.~\ref{fig:tc}. The plots in this figure confirm that the values of $m$ and $b$ correlate better for Alborz. Also included in Fig.~\ref{fig:azal-bm}, for reference, is the universal regression. While a direct comparison with the local regressions is not appropriate, the closer proximity of the Alborz trend line to the universal regression line suggests that the larger number of data points improves the quality of the regression, bringing it closer to the universal correlation line. The results for Kopeh Daght, not included here for brevity, show the poorest correlation, likely due to the least amount of data points, which reinforces the point made about the quality of the regression being dependent on a sufficiently large number of data points.}
